---
  title: "Exposure_analysis with all trials. Repetition del exp 1 corrigiendo error en timings"
author: "Alexis Perez-Bellido & Daniel Duato"
date: "5/22/2019"
output:
  pdf_document: default
html_document: default
---
  
  ## R Markdown
  Loading packages and setting paths
```{r}
root <- "/Users/alex/OneDrive - Universitat de Barcelona"
```

```{r, echo = FALSE}
library(readr)
library(ez)
library(retimes)
library(lemon)
library(lmerTest)
library(LMERConvenienceFunctions)
library(BayesFactor)
library(svglite)
library(tidyverse)
library(sjPlot)
setwd(paste(root,'/PROJECTS/MS_Statistical_learning/R/Exp_1rep', sep=""))
```

```{r}
mytheme <-  theme(axis.text=element_text(size=16), axis.title=element_text(size=14),axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 
```

# Analysing exposure Implicit task
Reading exposure data and properly code the variables
```{r}
xdata <- read_csv(paste(root,'/PROJECTS/MS_Statistical_learning/Behavioral/Exp_1rep/csv/exposure_all.csv', sep=""),col_types = cols())

xdata$subject = factor(xdata$subject, ordered=TRUE)
xdata$modality = factor(xdata$modality,labels=c("V","A"))
xdata$leading = factor(xdata$leading,labels=c("Leading","Trailing"))
xdata$pair_modality = factor(xdata$pair_modality, labels=c("AA","VV","AV","VA"))
xdata$next_mod = factor(xdata$next_mod,labels=c("V","A")) #the modality of the following stimulus (probably not useful)
xdata$modal_comb <- "multisensory" #Create variable. Conditions recoded into multimodal/unimodal
xdata$modal_comb[xdata$pair_modality == "AA" | xdata$pair_modality == "VV"] <- "unisensory"
xdata$stimulus = factor(xdata$stimulus)
xdata$pair = factor(xdata$pair)
xdata$mod_switch = factor(xdata$mod_switch, labels = c("Unimodal", "Crossmodal"))
xdata$detected = as.integer(xdata$detected)
# creating a variable to subdivide the experiment in 4 parts (of 2 blocks each)
xdata$part <- 1
#xdata$part[xdata$block > 2] <- 2
#xdata$part[xdata$block > 4] <- 3
xdata$part[xdata$block > 4] <- 2
head(xdata)
```

xdata %>%  group_by(subject, pair) %>% summarise(length(rt))


Looking at the impact of stimulus type on detection
```{r}
oddball <- subset(xdata, oddball == 1)
oddball$irt <- 1/oddball$rt
stim_detec <- oddball %>% group_by(stimulus) %>% mutate(hits = mean(detected))

ggplot(subset(oddball), aes(x=as.numeric(stimulus), y=as.numeric(detected), col = modality)) + 
 # scale_color_manual( values =  c("blue","orange"))+ scale_fill_manual( values =  c("blue","orange")) + 
  geom_point( data = stim_detec, aes(x = stimulus, y = hits), col = "black" ) + geom_smooth() + ylab("P(Hits)") + xlab("stim ID") + 
  theme_bw(20) + mytheme + ggtitle("Stimulus detection") + ylim(c(0.0, 1)) + theme(axis.text = element_text(size = 12),element_line(size = 0.3))    
ggsave(paste(root,'/PROJECTS/MS_Statistical_learning/Doc/MSLmanuscript/figures_results/exp1_stim.svg', sep=""), width=8, height=4) 
```



Propotion of erroneous 300 ms gaps per condition (they have to be 250ms)
```{r eval=FALSE, include=FALSE}
stim_gaps <- oddball %>% group_by(modality, mod_switch, leading) %>% summarise(gap = mean(gap))
stim_gaps 

ggplot(subset(xdata), aes(x=(as.numeric(onset)), y=oddball, col = factor(block))) + geom_point(alpha = 0.5, size = 0.002)  + theme_bw(20) + mytheme 
```

```{r}
min(subset(oddball, detected ==1)$rt)
```



```{r}

stim_detec_leading <- oddball %>% group_by(subject, modality, mod_switch, leading ) %>%  summarise(hits =mean(detected), irts = mean(irt[detected == 1]))

              
hit_SE_data <- Rmisc::summarySEwithin(stim_detec_leading, measurevar="hits", withinvars=c("modality","mod_switch", "leading"), idvar="subject") 
rt_SE_data <- Rmisc::summarySEwithin(stim_detec_leading, measurevar="irts", withinvars=c("modality","mod_switch", "leading"), idvar="subject") 


ggplot(subset(stim_detec_leading), aes(x=factor(leading), y=hits, col = factor(leading))) + 
  facet_rep_grid(modality~mod_switch) + geom_line(data=stim_detec_leading,aes(leading,hits,group = subject), alpha = 0.5, col = "darkgrey", size = 0.3) +  theme_bw(20) + ylab("P(Hits)") + xlab("Modality") +  mytheme +  scale_color_manual( values =  c("orange","darkgreen")) + scale_fill_manual( values =  c("orange","darkgreen")) +  geom_point( size = 2, alpha = 0.5, position = position_jitter(w = 0.25, h = 0)) + theme(axis.text = element_text(size = 12),element_line(size = 0.3))+  geom_errorbar(data = hit_SE_data, aes(ymax =  hits+se, ymin= hits-se), col = 'black',  width=0.5,size=0.3) +
 scale_y_continuous(limits=c(0.4,1.1), breaks = c(0.5, 0.75, 1)) 

ggsave("/Users/alex/Dropbox/Projects/MS_Statistical_learning/Doc/MSLmanuscript/figures_results/exp1_hits.svg", width=8, height=5) 

ggplot(subset(stim_detec_leading), aes(x=factor(leading), y=irts, fill = factor(leading), col = factor(leading))) + 
  geom_line(data=stim_detec_leading,aes(leading,irts,group = subject), alpha = 0.5, col = "darkgrey", size = 0.3) + 
  facet_rep_grid(modality~mod_switch) + theme_bw(20) + ylab("1/RT") + xlab("Modality") +  mytheme +
  scale_color_manual( values =  c("orange","darkgreen")) + scale_fill_manual( values =  c("orange","darkgreen")) +
  geom_point(  size = 2, alpha = 0.5, position = position_jitter(w = 0.25, h = 0)) + #
  geom_errorbar(data = rt_SE_data, aes(ymax =  irts+se, ymin= irts-se), col = 'black', width=0.5,size=0.3) + theme(axis.text = element_text(size = 12),element_line(size = 0.3))    + ylab("1/RT (s)") + scale_y_continuous(limits=c(1.2,3), breaks = c(1.5, 2, 2.5, 3))  

ggsave("/Users/alex/Dropbox/Projects/MS_Statistical_learning/Doc/MSLmanuscript/figures_results/exp1_rts.svg", width=8, height=5) 
```


# Creating some bins to plot the data
```{r}
oddball <-  oddball %>% group_by(subject ) %>%  mutate(bin = ntile(onset, 8))


stim_detec_subjbins <- oddball %>% group_by( modality, mod_switch, leading, subject, bin ) %>%  summarise(hits = mean(detected), irts = mean(irt[detected == 1]))

stim_detec_bins <- oddball %>% group_by( modality, mod_switch, leading, bin ) %>%  summarise(hits = mean(detected), irts = mean(irt[detected == 1]))
```




# Model for plotting
```{r}
rt.m3 <- lmer(irt ~  mod_switch * modality * onset  * leading + (1  | subject)   , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1))
summary(rt.m3)
```

```{r}

plot_model(rt.m3, show.values = TRUE, value.offset = .4)
```
```{r}
library(sjPlot)
sjp.lmer(rt.m3)
```


coefs(rt.m3)
```{r}
ggplot(subset(scaled_oddball,detected == 1), aes(x=(onset), y=irt, col =leading,  type = subject, fill = (leading)))  +  facet_rep_grid(modality~mod_switch) + coord_capped_cart(bottom='both', left='both') + theme_bw() + theme(panel.border=element_blank(), axis.line=element_line(),element_line(size = 0.3)) + scale_color_manual( values =   c("orange","darkgreen")) + scale_fill_manual( values =  c("orange","darkgreen")) + theme_bw(10) + mytheme  + 
  geom_line(aes(y = predict(rt.m3)),size=0.5, alpha = 0.5)  +
#scale_y_continuous(limits=c(0.25,3.5,4), breaks = c(0.5, 1.5, 2.5, 3.5)) + 
  theme(axis.text = element_text(size = 10),element_line(size = 0.3)) +
  scale_x_continuous(limits=c(-2.1,2.1), breaks = seq(-2,2, by = 1) ) + 
  xlab("Scaled onset time") + ylab("1/RT(s)")

ggsave(paste(root,'/PROJECTS/MS_Statistical_learning/Doc/MSLmanuscript/figures_results/exp1_lmm_rts.svg', sep=""), width=5, height=3) 

```

  
```{r}
ggplot(subset(stim_detec_bins), aes(x=(bin), y=irts, col =leading, fill = (leading)))  +  facet_rep_grid(modality~mod_switch) + coord_capped_cart(bottom='both', left='both') + theme_bw() + theme(panel.border=element_blank(), axis.line=element_line(),element_line(size = 0.3)) + scale_color_manual( values =   c("orange","darkgreen")) + scale_fill_manual( values =  c("orange","darkgreen")) + theme_bw(10) + mytheme  +
      geom_smooth(data=subset(stim_detec_subjbins, leading == 'Leading'),aes(bin,irts, group = subject), col = 'orange', inherit.aes=FALSE, size = 0.1, method=lm,  se = F, alpha = 0.05) +
      geom_smooth(data=subset(stim_detec_subjbins, leading == 'Trailing'),aes(bin,irts, group = subject), col = 'darkgreen', inherit.aes=FALSE, size = 0.1, method=lm,  se = F, alpha = 0.05) + 
  # geom_point(data=stim_detec_subjbins,aes(bin,irts, col = leading), alpha = 0.3, size = 0.3, position = position_jitter(w = 0.35, h = 0)) + 
  geom_smooth(method=lm,  se = F, size = 1) + geom_point( size = 1) +
scale_y_continuous(limits=c(0.25,3.5,4), breaks = c(0.5, 1.5, 2.5, 3.5)) + theme(axis.text = element_text(size = 8),element_line(size = 0.3)) +
  scale_x_continuous(limits=c(0,8), breaks = seq(1,8, by = 1) ) + xlab("Bins") + ylab("1/RT(s)")
ggsave("/Users/alex/Dropbox/Projects/MS_Statistical_learning/Doc/MSLmanuscript/figures_results/exp1_linear_rts.svg", width=5, height=4) 
```


Linear mixed models

Reescaling independent variable
```{r}
# Scale
scaled_oddball <- oddball
scaled_oddball$onset <- scale(scaled_oddball$onset) # lets re-scale the onset times to match the 0-1

```

Hits analyses
Can people learn visual contigencies



```{r}

hits.m <- glmer((detected) ~    (1  | subject) + (1 |stimulus) ,family = binomial(link = "logit") , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball))

hits.m0 <- glmer((detected) ~    modality + (1  | subject) + (1 |stimulus) ,family = binomial(link = "logit") , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball))

hits.m0b <- glmer((detected) ~    mod_switch + (1  | subject) + (1 |stimulus) ,family = binomial(link = "logit") , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball))

anova(hits.m,hits.m0,hits.m0b)
summary(hits.m0)

```




```{r}
hits.m <- glmer((detected) ~    (1  | subject) + (1 |stimulus) ,family = binomial(link = "logit") , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball))

hits.m0 <- glmer((detected) ~    modality + (1  | subject) + (1 |stimulus) ,family = binomial(link = "logit") , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball))

hits.m0b <- glmer((detected) ~    mod_switch + (1  | subject) + (1 |stimulus) ,family = binomial(link = "logit") , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball))

anova(hits.m,hits.m0,hits.m0b)
summary(hits.m0)

hits.m1 <- glmer((detected) ~   modality + onset + (1  + onset| subject) + (1 |stimulus) ,family = binomial(link = "logit") , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball))

anova(hits.m0, hits.m1)

summary(hits.m1)

hits.m2 <- glmer((detected) ~   modality * onset + (1 + onset  | subject) + (1 |stimulus) ,family = binomial(link = "logit") , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball,))

anova(hits.m1, hits.m2)

summary(hits.m3)

```


```{r}
hits.VV <- glmer(detected ~  leading * onset    + (1 + onset | subject) + (1 |stimulus),family = binomial(link = "logit")  , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball,  modality == "V" & mod_switch == "Unimodal"))
summary(hits.VV)

hits.AA <- glmer(detected ~  leading * onset    + (1 + onset | subject) + (1 |stimulus),family = binomial(link = "logit")  , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball,  modality == "A" & mod_switch == "Unimodal"))
summary(hits.AA)


hits.VA <- glmer(detected ~  leading * onset    + (1 + onset | subject) + (1 |stimulus) ,family = binomial(link = "logit") , control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball,  modality == "A" & mod_switch == "Crossmodal"))
summary(hits.VA)

hits.AV <- glmer(detected ~  leading * onset    + (1  + onset | subject) + (1 |stimulus) ,family = binomial(link = "logit"),  control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, modality == "V" & mod_switch == "Crossmodal"))
summary(hits.AV)

```

```{r}

rt.m <- lmer(irt ~   (1  | subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1))

rt.m0 <- lmer(irt ~   modality   + (1  | subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1))

rt.m0b <- lmer(irt ~   mod_switch   + (1  | subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1))

rt.m1 <- lmer(irt ~  modality + mod_switch   + (1  | subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1))

anova(rt.m,rt.m0,rt.m0b,rt.m1)

rt.m2 <- lmer(irt ~  modality * mod_switch   + (1  | subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1))

anova(rt.m1, rt.m2)

summary(rt.m2)

```


```{r}

rt.VV1 <- lmer(irt ~   onset    + (1  + onset | subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1 & modality == "V" & mod_switch == "Unimodal"))

rt.VV2 <- lmer(irt ~  leading * onset    + (1  + onset| subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1 & modality == "V" & mod_switch == "Unimodal"))

anova(rt.VV1,rt.VV2)

summary(rt.VV2)


rt.AA1 <- lmer(irt ~   onset    + (1  + onset| subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1 & modality == "A" & mod_switch == "Unimodal"))

rt.AA2 <- lmer(irt ~  leading * onset    + (1  + onset| subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1 & modality == "A" & mod_switch == "Unimodal"))

anova(rt.AA1, rt.AA2)

summary(rt.AA2)

rt.VA1 <- lmer(irt ~   onset    + (1  + onset| subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1 & modality == "A" & mod_switch == "Crossmodal"))

rt.VA2 <- lmer(irt ~  leading * onset    + (1  + onset| subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1 & modality == "A" & mod_switch == "Crossmodal"))
summary(rt.VA2)

anova(rt.VA1,rt.VA2)

rt.AV1 <- lmer(irt ~   onset    + (1  + onset| subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1 & modality == "V" & mod_switch == "Crossmodal"))

rt.AV2 <- lmer(irt ~  leading * onset    + (1  + onset| subject) + (1 |stimulus)  , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)) , data=subset(scaled_oddball, detected == 1 & modality == "V" & mod_switch == "Crossmodal"))
anova(rt.AV1,rt.AV2)
summary(rt.AV2)
```



# Analysing Explicit task

Loading explicit test data
```{r}


test <- read_csv(paste(root,'/PROJECTS/MS_Statistical_learning/Behavioral/Exp_1rep/csv/test_results.csv', sep = ""),col_types = cols())

test$modal_comb = factor(test$modality, labels=c("AA","VV","AV","VA"))
test$modal_comb <- factor(test$modal_comb,levels(test$modal_comb)[c(2,1,4,3)])
test$modality <- factor(test$modality, labels=c("Auditory","Visual","Visual","Auditory"))
test$modality <- factor(test$modality,levels(test$modality)[c(2,1,4,3)])
#test$trial_type = factor(test$trial_type, labels=c("Normal", "Inverted"))
test$multimodal = factor(test$multimodal, labels=c("Unimodal", "Multimodal"))
test$leading_modality = factor(test$leading_modality, labels=c("Visual", "Auditory"))
test$subject = factor(test$subject)
test$rkg_f = factor(test$rkg, labels=c("Remember","Know","Guess"))
test$when = cut(test$order,3, labels=c("Start","Middle","End"))
test$answer = factor(test$answer, labels=c("First","Second"))
test$trial_id = factor(test$trial_id)
std_pair_id = factor(test$std_pair_id)

test$rkg_f <-relevel(test$rkg_f,"Remember")
test$rkg_f <-relevel(test$rkg_f,"Know")
test$rkg_f <-relevel(test$rkg_f,"Guess")

```



```{r}


avg_test_xmod <- test %>% group_by(multimodal, modality, subject)  %>% summarise(correct= mean(correct))

#ezANOVA(avg_test_xmod, dv=.(correct), wid = .(subject), within = .( modality))

ggplot(subset(avg_test_xmod ), aes(x=factor(multimodal ), y=correct, col = factor(modality), fill = factor(modality))) + geom_violin(col = NA, alpha = 0.3,trim=FALSE) + facet_grid(modality~.) +
 theme_bw(20) + ylab("Accuracy") + xlab("Modality") + mytheme +
  geom_point( position = position_jitter(w = 0.2, h = 0)) + geom_boxplot( coef = 2, outlier.size=0 , col = "black", fill="NA", width = 0.2)  + scale_y_continuous(limits=c(0,1), breaks = c(0, 0.5, 1)) + geom_abline(intercept = 0.5, slope = 0)   + geom_smooth(data=avg_test_xmod,aes(multimodal,correct, group = subject), col = 'grey', inherit.aes=FALSE, size = 0.2, method=lm,  se = F, alpha = 0.1)



```
```{r}
fitchanceV <- glmer(correct ~   (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test, modality == "Visual" & multimodal == "Unimodal" ))
fitchanceV1 <- glmer(correct ~ rkg_f + (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test, modality == "Visual" & multimodal == "Unimodal" ))
summary(fitchanceV )
anova(fitchanceV,fitchanceV1)



fitchanceA <- glmer(correct ~   (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test, modality == "Auditory" & multimodal == "Unimodal" ))
fitchanceA1 <- glmer(correct ~ rkg_f + (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test, modality == "Auditory" & multimodal == "Unimodal" ))
summary(fitchanceA)
anova(fitchanceA,fitchanceA1)
summary(fitchanceA1 )

fitchanceAV <- glmer(correct ~   (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test, modality == "Visual" & multimodal == "Multimodal" ))
fitchanceAV1 <- glmer(correct ~ rkg_f + (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test, modality == "Visual" & multimodal == "Multimodal" ))
anova(fitchanceAV,fitchanceAV1)
summary(fitchanceAV)


fitchanceVA <- glmer(correct ~   (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test, modality == "Auditory" & multimodal == "Multimodal" ))
fitchanceVA1 <- glmer(correct ~ rkg_f + (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test, modality == "Auditory" & multimodal == "Multimodal" ))
anova(fitchanceVA,fitchanceVA1)
summary(fitchanceVA)

```




```{r}
avg_test_xmodrkgf  <- summarySEwithin(test, measurevar="correct", withinvars=c("multimodal","modality","rkg_f"), idvar="subject") 

#avg_test_xmodrkgf <- test %>% group_by(multimodal, modality, rkg_f)  %>% summarise(correct= mean(correct))

ggplot(subset(avg_test_xmodrkgf), aes(x=factor(rkg_f), y=correct, fill = (modality))) + geom_bar(stat="identity", position = "dodge") + facet_grid(multimodal~modality) + mytheme + scale_y_continuous(limits=c(0,1), breaks = c(0, 0.5, 1)) + geom_abline(intercept = 0.5, slope = 0) + theme(axis.text.x = element_text(angle = 40, hjust = 1, size =10))
```



```{r}


#ezANOVA(avg_test_xmod, dv=.(correct), wid = .(subject), within = .( modality))

ggplot(subset(avg_test_xmodrkgf ), aes(x=factor(rkg_f), y=correct, col = factor(modality), fill = factor(modality))) + geom_violin(col = NA, alpha = 0.3,trim=FALSE) + facet_grid(multimodal~modality)  +
 theme_bw(20) + ylab("Accuracy") + xlab("Modality") + mytheme +
  geom_point( position = position_jitter(w = 0.2, h = 0)) + geom_boxplot( coef = 2, outlier.size=0 , col = "black", fill="NA", width = 0.2)  + scale_y_continuous(limits=c(0,1), breaks = c(0, 0.5, 1)) + geom_abline(intercept = 0.5, slope = 0)


# logistic regression comparing intercepts is more appropiated
test$modality <-relevel(test$modality,"VV")
fitchance <- glmer(correct ~ modality  + (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test))
summary(fitchance )


# Converting the predicted value from log odds into percentage using the formula below
# exp(0.32152) / (1+exp(0.32152) )  # to get the intercept probabilities


test$modality <-relevel(test$modality,"AA")
fitchance <- glmer(correct ~ modality  + (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test))
summary(fitchance )
# 
# test$modality <-relevel(test$modality,"AV")
# fitchance <- glmer(correct ~ modality  + (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test))
# summary(fitchance )
# 
# 
# test$modality <-relevel(test$modality,"VV")
# fitchance <- glmer(correct ~ modality  + (1 | subject)  ,family = binomial(link = "logit")  , data=subset(test))
# summary(fitchance )
```

t.test(subset(avg_test_xmod, modality == "VV")$correct, mu = 0.5)

```{r}


avg_test_xmodxrkg <- test %>% group_by(multimodal, modality, rkg,  subject)  %>% summarise(correct= mean(correct))

#ezANOVA(avg_test_xmod, dv=.(correct), wid = .(subject), within = .( modality))

ggplot(subset(avg_test_xmodxrkg), aes(x=factor(rkg), y=correct, col = factor(modality), fill = factor(modality))) + geom_violin(col = NA, alpha = 0.3,trim=FALSE) +
 theme_bw(20) + ylab("Accuracy") + xlab("Modality") + mytheme + facet_grid(multimodal~modality) +
  geom_point( position = position_jitter(w = 0.2, h = 0)) + geom_boxplot( coef = 2, outlier.size=0 , col = "black", fill="NA", width = 0.2)  + scale_y_continuous(limits=c(0,1), breaks = c(0, 0.5, 1)) + geom_abline(intercept = 0.5, slope = 0)



```



```{r}
fitnomultinolead <- glmer(correct ~ rkg_f  + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test, modality == "AV"))
summary(fitnomultinolead)
```




```{r}

# fitchancerkg <- glmer(correct ~ modality + rkg_f + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test))
# summary(fitchancerkg)
# anova(fitchancerkg)
fitnomultinolead <- glmer(correct ~ rkg_f  + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test))
summary(fitnomultinolead)

fitmulti <- glmer(correct ~ rkg_f * multimodal + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test))
summary(fitmulti)
#anova(fitnomulti,fitmulti)

fitleading <- glmer(correct ~ rkg_f *leading_modality + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test))

anova(fitnomultinolead, fitleading )
# It seems that there is an effect of multisensory modality that interacts with ranking - know, and it is independent of the leading modality

ggplot(subset(avg_test_xmodrkg ), aes(x=factor(rkg_f), y=correct, col = (nobs), fill = (nobs))) + geom_bar(stat="identity", position = "dodge") + facet_grid(.~modality) + mytheme + scale_y_continuous(limits=c(0,1), breaks = c(0, 0.5, 1)) + geom_abline(intercept = 0.5, slope = 0) + theme(axis.text.x = element_text(angle = 40, hjust = 1, size =10))

# manually binomial tests per conditions

binomial_tests <- test %>% group_by(multimodal, modality, leading_modality, rkg_f)  %>% summarise(nobs = length(correct), correct = length(correct[correct==1])) %>% rowwise() %>% mutate(pvalue = binom.test(correct, nobs, p = 0.5, alternative = c("two.sided"), conf.level = 0.95)$p.value) 

p.adjust(binomial_tests$pvalue, method = "hochberg")



test$modality <-relevel(test$modality,"VV")
test$rkg_f <-relevel(test$rkg_f,"Know")
fitVVsimple <- glmer(correct ~ (1 | subject) ,family = binomial(link = "logit")  , data=subset(test, modality == "VV"))

fitVV <- glmer(correct ~ rkg_f + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test, modality == "VV"))
summary(fitVV)

# comparing VV model with rankings
anova(fitVVsimple,fitVV)


test$modality <-relevel(test$modality,"VV")
test$rkg_f <-relevel(test$rkg_f,"Remember")
fitVV <- glmer(correct ~ rkg_f + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test, modality == "VV"))
summary(fitVV)


test$modality <-relevel(test$modality,"AA")
test$rkg_f <-relevel(test$rkg_f,"Know")
fitAA <- glmer(correct ~ rkg_f + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test, modality == "AA"))
summary(fitAA)

test$modality <-relevel(test$modality,"AA")
test$rkg_f <-relevel(test$rkg_f,"Remember")
fitAA <- glmer(correct ~ rkg_f + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test, modality == "AA"))
summary(fitAA)

test$modality <-relevel(test$modality,"AA")
test$rkg_f <-relevel(test$rkg_f,"Guess")
fitAA <- glmer(correct ~ rkg_f + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test, modality == "AA"))
summary(fitAA)



fitAA <- glmer(correct ~ rkg_f + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test, modality == "AA"))
summary(fitAA)

fitVV <- glmer(correct ~ rkg_f + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test, modality == "VV"))
summary(fitVV)

fitchanceXrkg <- glmer(correct ~ modality * rkg_f + (1 | subject) ,family = binomial(link = "logit")  , data=subset(test))
summary(fitchanceXrkg)




```


avg_data_subj <- aggregate(cbind(correct)~multimodal+modality+subject , data = subset(test), mean)
t.test(subset(test, modality == "AA")$correct, mu = 0.5)
avg_data <- aggregate(cbind(correct)~multimodal+modality , data = subset(test), mean)
print(avg_data)

avg_data <- aggregate(cbind(correct)~multimodal+modality+rkg , data = subset(test), length)
print(avg_data)

binom.test(20, 35, p = 0.5,
           alternative = c("two.sided"),
           conf.level = 0.95)

binom.test(20, 35, p = 0.5,
           alternative = c("two.sided"),
           conf.level = 0.95)
           
           
Por ahora los resultados parecen indicar que la gente solo aprende los auditivos, tan unimodales como multimodales, esto se manifiesta de forma implicita en RTs. Aunque solo aprenden de forma explicita los auditivos


```

